Covariate analysis of ROSMAP RNASeq

### 2016-01-26 code/Rmd/ROSMAP_RNASeq.Rmd
Minor modifications

# Find significant covariates
adjustCovars = designMatVarsToCovars(getCovariatesMap(DM),preAdjustedSigCovars$significantCovars)
```
Significant covariates to adjust at FDR 0.1 are `r adjustCovars`
```{r preAdjustedSigCovars.NULL.ALL, fig.width=10, fig.height=6}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```
### Normalisation (custom design)
Fitting a linear model with cogdx, Batch, RINcontinuous, and pmi 
```{r iterative.normalisation, cache=TRUE, results='asis', echo=FALSE}
postAdjustCovars <- c('cogdx', 'Batch', 'RINcontinuous', 'pmi')

>>>>

# Find significant covariates
adjustCovars = designMatVarsToCovars(getCovariatesMap(DM),preAdjustedSigCovars$significantCovars)
```
Significant covariates to adjust at FDR 0.1 are `r adjustCovars`
```{r preAdjustedSigCovars.NULL.ALL, fig.width=15, fig.height=8}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```
### Normalisation (custom design)
Fitting a linear model with cogdx, Batch, RINcontinuous, and pmi 
```{r iterative.normalisation, cache=TRUE, results='asis', echo=FALSE}
postAdjustCovars <- c('cogdx', 'Batch', 'RINcontinuous', 'pmi')
